### 2016-03-18 papers.tex
papers.tex: Stamp the three pages whose artifacts have been reviewed

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{0cm}
	{}
\addreview{paper18eval}{-1.45cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

@@

\addtrack{Rototiller track}{Overcomplexity Theory}
\addpaper
	{The computational complexity of Chinese and Italian noodle making}
	{Daniel M.\ Berry and Luisa Mich}
	{algorithm, Chinese mian, computational complexity, Italian pasta, noodle}
	{SIGBOVIK_2016_paper_2}
	{0cm}
	{}
\addreview{paper2review}{0cm}
\addpaper
	{Which ITG stepcharts are turniest?}
	{Ben Blum}
	{in, the, groove}
	{SIGBOVIK_2016_paper_12}
	{0cm}
	{}
\addreview{paper12eval}{-1.45cm}

@@

\addtrack{Garbage track}{Reduce, Reuse, Recycle}
\addpaper
	{PRESS RELEASE: FOR IMMEDIATE WORLDWIDE RELEASE}
	{Nicholas Fudala and Chester Francis}
	{editors note, this didnt seem very important, so we sat on it for 2 years, with love, the ach committee for retrocausal publication impact}
	{SIGBOVIK_2016_paper_17}
	{0cm}
	{}
\addpaper
	{Pittsburgh is a grid}
	{Stefan Muller}
	{Pittsburgh, grids, unnecessary integrals, computational geography}
	{SIGBOVIK_2016_paper_10}
	{-0.3cm}
	{}
\addreview{paper10eval}{-1.35cm}

>>>>

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper18eval}{-1.45cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

@@

\addtrack{Rototiller track}{Overcomplexity Theory}
\addpaper
	{The computational complexity of Chinese and Italian noodle making}
	{Daniel M.\ Berry and Luisa Mich}
	{algorithm, Chinese mian, computational complexity, Italian pasta, noodle}
	{SIGBOVIK_2016_paper_2}
	{0cm}
	{}
\addreview{paper2review}{0cm}
\addpaper
	{Which ITG stepcharts are turniest?}
	{Ben Blum}
	{in, the, groove}
	{SIGBOVIK_2016_paper_12}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper12eval}{-1.45cm}

@@

\addtrack{Garbage track}{Reduce, Reuse, Recycle}
\addpaper
	{PRESS RELEASE: FOR IMMEDIATE WORLDWIDE RELEASE}
	{Nicholas Fudala and Chester Francis}
	{editors note, this didnt seem very important, so we sat on it for 2 years, with love, the ach committee for retrocausal publication impact}
	{SIGBOVIK_2016_paper_17}
	{0cm}
	{}
\addpaper
	{Pittsburgh is a grid}
	{Stefan Muller}
	{Pittsburgh, grids, unnecessary integrals, computational geography}
	{SIGBOVIK_2016_paper_10}
	{-0.3cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper10eval}{-1.35cm}
